Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy\\ \thanks{Grantee Capes.}

### 2023-09-27 Text/Articles/MIGARS_2024/migars2024_abstract.tex
hypothesis testing

Suppose a random variable $X$ has a distribution function $F(x)$ with a continuous density function $f(x)$. Then, the Shannon entropy $H(X)$ is defined as
\begin{equation*}
  %\label{E:entropy2}
  H(X)=-\int_{-\infty }^\infty \ f(x)\log(f(x))\,dx.
\end{equation*}
The problem of estimating $H(X)$ has been considered by many authors including \cite{vasicek1976test, van1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.

@@

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{van1992}, who proposed a new estimator of entropy given by

>>>>

Suppose a random variable $X$ has a distribution function $F(x)$ with a continuous density function $f(x)$. Then, the Shannon entropy $H(X)$ is defined as
\begin{equation*}
  %\label{E:entropy2}
  H(X)=-\int_{-\infty }^\infty \ f(x)\log(f(x))\,dx.
\end{equation*}
The problem of estimating $H(X)$ has been considered by many authors including \cite{vasicek1976test, Bert1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.

@@

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{Bert1992}, who proposed a new estimator of entropy given by
